### 2018-12-11 paper/main.tex
Workers parameter. IRNV2 freeze conv layers

	\begin{itemize}
		\item \textit{Logit}. Logit link function is the most widely used function for Proportional Odds Models. These kind of models are also called Cummulative Logit Models. The logit link is shown in Eq. \ref{eq:logit}.
		\begin{equation}
		\small
		logit[P(Y_i \le j)] = \alpha_j + \beta'x_i,\quad j = 1, ..., c - 1
		\label{eq:logit}
		\end{equation}
		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf). Its expression is shown in Eq. \ref{eq:probit}.	
		\begin{equation}
		\small
		\Phi^-1[P(Y \le j)] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
		\label{eq:probit}
		\end{equation}
		\item \textit{Complementary log-log}. Unlike logit and probit, complementary log-log function is not symmetric. With a continuous predictor $x$, for example, $P(Y \le j)$ approaches 0 at a different rate than it approaches 1. Complementary log-log expression is shown in Eq. \ref{eq:cloglog}.
		\begin{equation}
		\footnotesize
		log[-log[1 - P(Y \le j)]] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
		\label{eq:cloglog}
		\end{equation}
	\end{itemize}

@@

	\begin{table}[H]
		\footnotesize
		\centering
		\begin{tabular}{ccc|cc}
			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
			$5$ & $10^{-2}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$\\
			& $10^{-3}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$\\
			& $10^{-4}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$\\
			$10$ & $10^{-2}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$\\
			& $10^{-3}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$\\
			& $10^{-4}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$\\
			$15$ & $10^{-2}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$\\
			& $10^{-3}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$\\
			& $10^{-4}$ & Logit & $-$ & $-$\\
			& & Probit & $-$ & $-$\\
			& & c log-log & $-$ & $-$
		\end{tabular}
		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
		\label{table:Adienceresults}
	\end{table}

>>>>

	\begin{itemize}
		\item \textit{Logit}. Logit link function is the most widely used function for Proportional Odds Models. These kind of models are also called Cummulative Logit Models. The logit link is shown in Eq. \ref{eq:logit}.
		\begin{equation}
		\small
		logit[P(Y_i \le j)] = \alpha_j + \beta'x_i,\quad j = 1, ..., c - 1
		\label{eq:logit}
		\end{equation}
		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf). Its expression is shown in Eq. \ref{eq:probit}.	
		\begin{equation}
		\small
		\Phi^{-1}[P(Y \le j)] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
		\label{eq:probit}
		\end{equation}
		\item \textit{Complementary log-log}. Unlike logit and probit, complementary log-log function is not symmetric. With a continuous predictor $x$, for example, $P(Y \le j)$ approaches 0 at a different rate than it approaches 1. Complementary log-log expression is shown in Eq. \ref{eq:cloglog}.
		\begin{equation}
		\footnotesize
		log[-log[1 - P(Y \le j)]] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
		\label{eq:cloglog}
		\end{equation}
	\end{itemize}

@@

	\begin{table}[H]
		\footnotesize
		\centering
		\begin{tabular}{ccc|cc}
			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
			$5$ & $10^{-2}$ & Logit & $0.72072$ & $0.68408$\\
			& & Probit & $0.77608$ & $0.72574$\\
			& & c log-log & $0.7543$ & $0.70742$\\
			& $10^{-3}$ & Logit & $0.7146$ & $0.67868$\\
			& & Probit & $0.81906$ & $0.77154$\\
			& & c log-log & $0.57196$ & $0.55608$\\
			& $10^{-4}$ & Logit & $0.54432$ & $0.51934$\\
			& & Probit & $0.5436$ & $0.52422$\\
			& & c log-log & $0.54802$ & $0.52484$\\
			$10$ & $10^{-2}$ & Logit & $0.78872$ & $0.72994$\\
			& & Probit & $0.79332$ & $0.7475$\\
			& & c log-log & $0.78004$ & $0.7326$\\
			& $10^{-3}$ & Logit & $0.49686$ & $0.47112$\\
			& & Probit & $0.59778$ & $0.58476$\\
			& & c log-log & $0.52016$ & $0.49968$\\
			& $10^{-4}$ & Logit & $0.60972$ & $0.56814$\\
			& & Probit & $0.54638$ & $0.52632$\\
			& & c log-log & $0.75428$ & $0.52094$\\
			$15$ & $10^{-2}$ & Logit & $0.79104$ & $0.74388$\\
			& & Probit & $\textbf{0.84254}$ & $\textbf{0.78666}$\\
			& & c log-log & $0.78802$ & $0.74624$\\
			& $10^{-3}$ & Logit & $0.56946$ & $0.52978$\\
			& & Probit & $0.70262$ & $0.65416$\\
			& & c log-log & $0.49242$ & $0.4732$\\
			& $10^{-4}$ & Logit & $0.55202$ & $0.52484$\\
			& & Probit & $0.54288$ & $0.5174$\\
			& & c log-log & $0.53826$ & $0.52542$
		\end{tabular}
		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
		\label{table:Adienceresults}
	\end{table}
